\titel

### 2014-03-10 presentation/presa.tex
ff replan added

  Perks
  \begin{itemize}
    \item No efficient algorithmic methods are possible for PSPACE-complete planning, inspired to focus on being efficient on a restricted subclass
    \item Most domains in the IPCC are simple in their structure and can be easily solves using greedy algorithms like FF
  \end{itemize}

  Criticism
  \begin{itemize}
    \item Methods are motivated by observing example domains - might influence the completeness
    \item Pruning techniques are incomplete
    \item FF behaves poorly in domains with many dead-ends
    \item Solving these tasks with complete best-first search exhaust the memory for larger instances
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Problem
      \begin{itemize}
        \item MDPs have been the standard for probabilistic planning algorithms
        \item
      \end{itemize}
  \end{itemize}

>>>>

\begin{itemize}
\item  Perks
  \begin{itemize}
    \item No efficient algorithmic methods are possible for PSPACE-complete planning, inspired to focus on being efficient on a restricted subclass
    \item Most domains in the IPCC are simple in their structure and can be easily solves using greedy algorithms like FF
  \end{itemize}
\item Criticism
  \begin{itemize}
    \item Methods are motivated by observing example domains - might influence the completeness
    \item Pruning techniques are incomplete
    \item FF behaves poorly in domains with many dead-ends
    \item Solving these tasks with complete best-first search exhaust the memory for larger instances
  \end{itemize}
\end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Problem
	\begin{itemize}
        	\item MDPs have been the standard for probabilistic planning algorithms
        	\item MDPs can be computationally intensive
	\item typically enumerate the entire state and action space
      	\end{itemize}
   \item Motivation for the FF planner
	\begin{itemize}
	\item Technological development within processing units
	\item Relying on search introduces speed and efficiency
	\end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - details of the solution}

  \begin{itemize}
    \item The planning problem
	\begin{itemize}
        	\item a domain description
	\item a goal
	\item an initial state 
	\end{itemize}
   \item FF-replan
	\begin{itemize}
	\item Generates a deterministic planning problem
	\item Uses the FF planner to compute a totally-ordered plan
	\item If during execution an unexpected (not in the hash-table) occurs, the process is repeated using this as an initial state
	\end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - details of the solution}

  \begin{itemize}
    \item Determinization
	\begin{itemize}
        	\item Single outcome determinization
	\item All-outcomes determinization
	\end{itemize}
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - details of the solution}

  \begin{itemize}
    \item Determinization
   \item Planning
	\begin{itemize}
	\item Partial state-action mapping using an initial empty hash-table
	\item Unexpected states are determinized and the synthesized plan (by FF) is put in the hash table
	\end{itemize}

\emph{ insert image how hash table is filled}

   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Critism}

  \begin{itemize}
    \item Shortcomings
	\begin{itemize}
        	\item Probabilistic effects are treated as equal

\includegraphics[scale=0.5]{images/blindfold.jpg}

	\end{itemize}
   \item Means of improvement
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Critism}

  \begin{itemize}
    \item Shortcomings
	\begin{itemize}
        	\item Probabilistic effects are treated as equal
	\item Only works well if the outcomes are likely
\includegraphics[scale=0.5]{images/direction-road-maze.jpg}
	\end{itemize}
   \item Means of improvement

   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Critism}

  \begin{itemize}
    \item Shortcomings
	\begin{itemize}
        	\item Probabilistic effects are treated as equal
	\item Only works well if the outcomes are likely
\includegraphics[scale=0.01]{images/direction-road-maze.jpg}
	\end{itemize}
   \item Means of improvement
	\begin{itemize}
	\item
	\end{itemize}
   \end{itemize}
\end{frame}
